Marine species do not need visas: the transboundary nature of the world’s exploited marine species

### 2020-04-21 Scripts/Manuscript_Draft.Rmd
Re-organized folders

---
title: "Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada. ^2^Yale University, New Haven, Connecticut, USA. ^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
# subtitle: "[DRAFT DO NOT SHARE]"
subtitle: "Most neighbor nations share marine exploited species"
output:
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
  pdf_document:
    fig_caption: yes
geometry: margin=1in
editor_options:
  chunk_output_type: inline
bibliography: ./References/FishForVisa_Ref.bib
csl: ./References/nature_cc.csl
---

@@

```{r Ch2_setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

## Results and Discussion

@@

![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue. A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively. B) Contribution of transboundary species to regional revenue (left) and catch (right). Regions according to the United Nations sub-regions. Points = mean +- sd. Revenue in 2010 real USD.](./Figures/Fig1.png)

@@

![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/Fig2.png)

@@

![Figure 3. Number of transboundary species by catch category. Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](./Figures/Fig3.png)

@@

![Figure 4. Number of EEZs shared by transboundary species. A) Number of EEZs by species organized by associated habitat according to FishBase. Showing only species that share > 20 EEZs. B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](./Figures/Fig4.png)

@@

![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](./Figures/Fig5.png)

@@

Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*. The *Area Index* consist in the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ. We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution. This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig. S3).

@@

Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g. all datasets agree on presence) and at least 25% of *Area Index* (e.g. the species shared distribution was at least 25% in each EEZ). This presents a relative conservative estimate of the number of transboundary species in the world. However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Fig. S4).

@@

![Figure S1. Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](./Figures/FigS1.png)

@@

img <- readPNG(here("./Figures/S3_Area.png"))
grid.raster(img)
```

![Figure S2. Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)

>>>>

---
title: "Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada. ^2^Yale University, New Haven, Connecticut, USA. ^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
# subtitle: "[DRAFT DO NOT SHARE]"
output:
  pdf_document:
    fig_caption: yes
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
geometry: margin=1in
editor_options:
  chunk_output_type: inline
bibliography: ./References/FishForVisa_Ref.bib
csl: ./References/nature_cc.csl
---

@@

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

# Results and Discussion

@@

![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue. A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively. B) Contribution of transboundary species to regional revenue (left) and catch (right). Regions according to the United Nations sub-regions. Points = mean +- sd. Revenue in 2010 real USD.](~/GitHub/FishForVisa/Figures/Fig1.png)

@@

![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](~/GitHub/FishForVisa/Figures/Fig2.png)

@@

![Figure 3. Number of transboundary species by catch category. Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](~/GitHub/FishForVisa/Figures/Fig3.png)

@@

![Figure 4. Number of EEZs shared by transboundary species. A) Number of EEZs by species organized by associated habitat according to FishBase. Showing only species that share > 20 EEZs. B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](~/GitHub/FishForVisa/Figures/Fig4.png)

@@

![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](~/GitHub/FishForVisa/Figures/Fig5.png)

@@

Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*. The *Area Index* consist in the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ. We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution. This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig. S2).

@@

Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g. all datasets agree on presence) and at least 25% of *Area Index* (e.g. the species shared distribution was at least 25% in each EEZ). This presents a relative conservative estimate of the number of transboundary species in the world. However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Fig. S2).

@@

![Figure S1. Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](~/GitHub/FishForVisa/Figures/FigS1.png)

@@

img <- readPNG(here("./Figures/FigS4.png"))
grid.raster(img)
```

![Figure S2. Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS4.png)
